\documentclass{article}
\usepackage{fullpage}
\newcommand{\answerbox}{\vspace{1.5cm}}
\newcommand{\BE}{\begin{enumerate}}
\newcommand{\EE}{\end{enumerate}}
\newcommand{\I}{\item}
\begin{document}
\part*{1 Peter 2:13-17}

\BE
\section*{The command}
\I  What is the command given to us in verse 13? \answerbox
\I  In your own words, define ``submit'' (verse 13). 
    How is submission different than mere obedience? \answerbox
\I  How does verse 17 describe our duty to civil authorities?
    How does this differ from our relationship with fellow believers and God?
        \answerbox
\I  According to verses 13 and 14, in what cases does Peter's command apply?
    Are there exceptional cases where it does not apply? Give verses. 
        \answerbox
\I  According to verse 13, why are we to obey the command, and how does it 
        connect to verses 11 and 12, as seen by the word, ``Therefore''? 
        \answerbox
\I  What are some of the ordinances we must submit to today? 
    In what ways does our obedience to these ordinances bring glory to God? 
        \answerbox

\section*{The principle}
\I  What is God's plan for our lives, according to verse 15? \answerbox
\I  What are foolish men ignorant of, and how does our doing good silence
        their accusations? \answerbox
\I  In what way is the Christian free, as described in verse 16? \answerbox
\I  How can a carnal Christian use his freedom as a ``cloak for vice''?
        \answerbox
\I  How are obedient Christians to use their freedom in Christ as 
        ``bondservants of God''? 
    Consider especially the example of Paul in 1 Corinthians 9:19-23 and
        10:23-24. \answerbox
\I  What freedoms has God called you to renounce in order to serve Him more
        fully? \answerbox
\EE
\end{document}


