\documentclass[12pt]{article}
\newcommand{\BI}{\begin{enumerate}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{enumerate}}
\title{Work Day}
\begin{document}
\maketitle
Items are listed in order of \emph{approximate} priority. 
We probably won't come close to doing everything, that's okay.
You can ask me (Jesse) for clarification, if I'm not around my cell is (408) 568-9356.
\BI Main Sanctuary
    \BI Apply wood polish to pews
    \I  Vacuum pews and carpet
    \I  General cleaning (remove old bulletins...)
    \I  Replace pens with pencils
    \I  Restock visitor cards (remove old ones which have been written on) \EI
\I  Refinish exterior wood doors and paneling of main building (see Jesse for more details)
    \BI Remove doors from hinges
    \I  Sand using electric sander, then by hand
    \I  Apply finish to top and bottom
    \I  Re-hinge doors
    \I  Apply finish to remaining surfaces \EI
\I  Bathrooms: Regular cleaning and restocking
\I  Replace Air Filters of AC system (for both AC systems)
    \BI New filters likely need to be purchased. \EI
\I  Supply run
    \BI Colored paper for Sunday bulletins needs to be purchased \EI
\I  Annex
    \BI Sweep floors
    \I  Clean and restock bathroom (including better solution for hand soap) \EI
\I  Purchase and install rubber ring-boots for vent flashings (pipes sticking out of roof) near the roof by the main entrance of the main building.
    \BI Diameter of pipes (flashings) and approximate degree of roof need to first be measured in order to purchase the correct rubber boots.
    \I  Rubber boots then need to be installed. \EI
\I  Roof gutters in main building
    \BI  Clean gutters of debris \EI
\I  Park strips
    \BI  Check the park strips both at the front and back of the church for weeds and litter. \EI
\I  Water heater in main building
    \BI Purchase and install seismic restraint for the water heater of the main building
    \I  Purchase and install piping in order to route the Temperature/Pressure Relief valve (TPR valve) of the water heater to the adjacent floor sink. \EI
\I  Electrical Panel for main building
    \BI  The electrical panel (located “around the corner” from main entrance) has openings in it, which need to be covered. \EI
\EI
\end{document}
